### 2024-02-24 presentation/parts/introduction.tex
WIP

\begin{frame}
    \frametitle{Errors in medical dialogue}
    \begin{itemize}
        \item<1,2>Communication is everywhere in healthcare. 
        \item <1,2>It is complex, involving multiple participants, different contexts, and different purposes.
        \item <2> {\color{dtured} } Failure of communication is a leading cause of medical error contributing to two out of three adverse events \cite{starmer_changes_2014}.
        \item <2> A considerable fraction of all hospital admissions had preventable adverse outcomes (9\% to 16.6\% in AU, NZ, UK, DK) \cite{carver_medical_2024}.
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{How might machine learning help?}
    \begin{itemize}
        \item <1> {\color{dtured}Assist} with documentation.
        \item <1> {\color{dtured}Augment} communication.
        \item <1> {\color{dtured}Improve} decision-making.
        \vspace{1em}
        \item <1> {\color{dtured}Reduce} errors.
        \item <1> {\color{dtured}Save} time.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Reliability of machine learning}
    \begin{itemize}
        \item <1> {\color{dtured}Data}: Privacy, quality, quantity, diversity.
        \item <1> {\color{dtured}Interpretability}: Trust, ethics, regulation.
        \item <1> {\color{dtured}Explainability}: Transparency, accountability.
        \item <1> {\color{dtured}Robustness}: Adversarial attacks, distribution shift.
        \item <1> {\color{dtured}Bias}: Fairness, transparency.
        \item <1> {\color{dtured}Complexity}: Context, domain, language, culture.
    \end{itemize}

>>>>

\begin{frame}
    \frametitle{Errors in medical dialogue}
    \begin{itemize}
        \item<1,2>Communication is everywhere in healthcare. 
        \item <1,2>It is complex, involving multiple participants, different contexts, and different purposes.
        \vspace{1em}
        \item <2> {\color{dtured} Adverse events}: Failure of communication is a leading cause of medical error contributing to two out of three adverse events \cite{starmer_changes_2014}.
        \item <2> {\color{dtured} Preventability}: A considerable fraction of all hospital admissions had preventable adverse outcomes (9\% to 16.6\% in AU, NZ, UK, DK) \cite{carver_medical_2024}.
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{How might machine learning help?}
    \begin{itemize}
        \item <1-> {\color{dtured}Assist} with documentation.
        \item <1-> {\color{dtured}Augment} communication.
        \item <1-> {\color{dtured}Improve} decision-making.
        \vspace{1em}
        \item <2-> {\color{dtured}Reduce} errors.
        \item <2-> {\color{dtured}Free up} time for patient care.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Reliability of machine learning systems}
    \begin{itemize}
        \item <1-> {\color{dtured}Data}: Privacy, quality, quantity, diversity, bias.
        \item <2-> {\color{dtured}Task}: Context, domain, language, culture.
        \item <3-> {\color{dtured}Interpretability}: Trust, ethics, regulation, transparency, accountability.
        \item <3-> {\color{dtured}Explainability}: 
        \item <4-> {\color{dtured}Fairness} in treatment of different groups of people.
        \item <5-> {\color{dtured}Robustness} to noise, outliers, adversarial attacks, and distribution shift.
    \end{itemize}

### 2024-02-24 presentation/parts/overview_discussion.tex
WIP

                    \tikzmarkin<1->{hierarchical-8}(0.1,-0.3)(-0.1,0.4)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 4}}}         & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{hierarchical vaes know what they don't know}} & \tikzmarkend{hierarchical-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    \tikzmarkin<1->{brief-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<-1>{black!20}\makecell[l]{ \textsc{\itshape chapter 6}\\\\}}    & {\color<-1>{black!20} \bfseries \scshape \Large \makecell[l]{a brief overview of unsupervised speech \\representation learning}} & \tikzmarkend{brief-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    \tikzmarkin<1->{retrospective-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<1->{black!20}\makecell[l]{\textsc{\itshape chapter 9}\\\\}}     & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{a retrospective study on machine learning-\\assisted stroke recognition for medical helpline calls}} & \tikzmarkend{retrospective-8} \\
                    \addlinespace[0.5em]
                    \midrule
                    \addlinespace[0.5em]

                    & {\color<1->{black!20}\makecell[l]{\textsc{\itshape chapter 10}}}        & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{discussion and conclusion}} & \\
                \end{tabular}
                }
            \end{table}
        \end{column}
        \begin{column}{0.4\textwidth}
            \tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
            \tikzstyle{myrect} = [fill]
            \begin{figure}
                \centering
                \begin{overprint}
                    \onslide<1>\tikzhierarchical
                    \onslide<2>\tikzbrief
                \end{overprint}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

>>>>

                    \tikzmarkin<1->{hierarchical-8}(0.1,-0.3)(-0.1,0.4)
                    & {\color<1->{black!20}\makecell[l]{\textsc{\itshape chapter 4}}}         & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{hierarchical vaes know what they don't know}} & \tikzmarkend{hierarchical-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    \tikzmarkin<1->{brief-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<1->{black!20}\makecell[l]{ \textsc{\itshape chapter 6}\\\\}}    & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{a brief overview of unsupervised speech \\representation learning}} & \tikzmarkend{brief-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    \tikzmarkin<1->{retrospective-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 9}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{a retrospective study on machine learning-\\assisted stroke recognition for medical helpline calls}} & \tikzmarkend{retrospective-8} \\
                    \addlinespace[0.5em]
                    \midrule
                    \addlinespace[0.5em]

                    & {\color<-1>{black!20}\makecell[l]{\textsc{\itshape chapter 10}}}        & {\color<-1>{black!20} \bfseries \scshape \Large \makecell[l]{discussion and conclusion}} & \\
                \end{tabular}
                }
            \end{table}
        \end{column}
        \begin{column}{0.4\textwidth}
            \tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
            \tikzstyle{myrect} = [fill]
            \begin{figure}
                \centering
                \begin{overprint}
                    \onslide<1>\tikzretrospective
                    \onslide<2>\tikzoverview
                \end{overprint}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

### 2024-02-24 presentation/parts/overview_retrospective.tex
WIP

                    \tikzmarkin<1->{brief-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<1->{black!20}\makecell[l]{ \textsc{\itshape chapter 6}\\\\}}    & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{a brief overview of unsupervised speech \\representation learning}} & \tikzmarkend{brief-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    \tikzmarkin<1->{retrospective-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{black!20}\makecell[l]{\textsc{\itshape chapter 9}\\\\}}     & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{a retrospective study on machine learning-\\assisted stroke recognition for medical helpline calls}} & \tikzmarkend{retrospective-8} \\
                    \addlinespace[0.5em]
                    \midrule
                    \addlinespace[0.5em]

                    & {\color<-1>{black!20}\makecell[l]{\textsc{\itshape chapter 10}}}        & {\color<-1>{black!20} \bfseries \scshape \Large \makecell[l]{discussion and conclusion}} & \\
                \end{tabular}
                }
            \end{table}
        \end{column}
        \begin{column}{0.4\textwidth}
            \tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
            \tikzstyle{myrect} = [fill]
            \begin{figure}
                \centering
                \begin{overprint}
                    \onslide<1>\tikzretrospective
                    \onslide<2>\tikzoverview
                \end{overprint}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

>>>>

                    \tikzmarkin<1->{brief-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<2->{black!20}\makecell[l]{ \textsc{\itshape chapter 6}\\\\}}    & {\color<2->{black!20} \bfseries \scshape \Large \makecell[l]{a brief overview of unsupervised speech \\representation learning}} & \tikzmarkend{brief-8} \\
                    \addlinespace[0.5em]
                    \addlinespace[0.5em]

@@

                    \tikzmarkin<1->{retrospective-8}(0.1,-0.4)(-0.1,0.6)
                    & {\color<-1>{black!20}\makecell[l]{\textsc{\itshape chapter 9}\\\\}}     & {\color<-1>{black!20} \bfseries \scshape \Large \makecell[l]{a retrospective study on machine learning-\\assisted stroke recognition for medical helpline calls}} & \tikzmarkend{retrospective-8} \\
                    \addlinespace[0.5em]
                    \midrule
                    \addlinespace[0.5em]

                    & {\color<1->{black!20}\makecell[l]{\textsc{\itshape chapter 10}}}        & {\color<1->{black!20} \bfseries \scshape \Large \makecell[l]{discussion and conclusion}} & \\
                \end{tabular}
                }
            \end{table}
        \end{column}
        \begin{column}{0.4\textwidth}
            \tikzstyle{mybox} = [fill, rounded corners, minimum width=140, minimum height=20]
            \tikzstyle{myrect} = [fill]
            \begin{figure}
                \centering
                \begin{overprint}
                    \onslide<1>\tikzbrief
                    \onslide<2>\tikzretrospective
                \end{overprint}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}
